**NAME OF THIS STUDY**

### 2018-10-23 submission/manuscript.Rmd
trouble with confidence interval plot

pdf("../results/figures/LogReg_inR.pdf")
par(mar=c(4,4,1,1))
# Plot random line on ROC curve
plot(c(1,0),c(0,1),
     type='l',
     lty=3,
     xlim=c(1.01,0), ylim=c(-0.01,1.01),
     xaxs='i', yaxs='i',
     ylab='', xlab='')
# Plot Test ROC in black line
plot(test_roc,
     col='black',
     lwd=2,
     add=T,
     lty=1)
#Calculate Confidence Interval sensitivities at given specificities
sens.ci <- ci.se(test_roc)
# Calculate CI for AUC values
auc_ci <- test_roc$ci[3]-test_roc$ci[2]

>>>>

pdf("../results/figures/LogReg_inR.pdf")
par(mar=c(4,4,1,1))
# Plot random line on ROC curve
plot(c(1,0),c(0,1),
     type='l',
     lty=3,
     xlim=c(1.01,0), ylim=c(-0.01,1.01),
     xaxs='i', yaxs='i',
     ylab='', xlab='')
# Plot Test ROC in black line
plot(test_roc,
     col='black',
     lwd=2,
     add=T,
     lty=1)
#Calculate Confidence Interval sensitivities at given specificities
sens.ci <- ci.se(test_roc, 
          specificities=seq(0, 100, 5)) # over a select set of specificities

# Calculate CI for AUC values
auc_ci <- test_roc$ci[3]-test_roc$ci[2]
